---
date: Sys.Date()
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    fig_crop: FALSE
graphics: yes
header-includes:
  - \usepackage{booktabs}
  - \usepackage{caption}
params:
  spp: NA
  sppCode: NA
  cntry: NA
  cntryAbbr: NA
  date: NA
  rootDir: NA
  save: FALSE
fontsize: 14pt
---

```{r}
cntryAbbr="MX"
cntry="Mexico"
sppCode = "ANTROZOUS_PALLIDUS"
spp = "Antrozous pallidus"
date = "20221116"
threats <- read.csv(paste0(here::here(), '/Data/ThreatNum.csv'))
DataFolder = paste0(here::here(), '/Data/derived/AnalysisExport_', date)
thisRangeFN <- paste0(here::here(), '/RangeGraphs/range_', spp,  "_", cntry, '.png')
```


```{r setup, include=FALSE, echo=F}
library(dplyr)
library(tidyr)
require(ggplot2)
require(ggpubr)
knitr::opts_chunk$set(echo = FALSE, message= FALSE, warning= FALSE)
options(scipen = 999)
knitr::knit_hooks$set(
  inline = function(x) {
    if (!is.numeric(x)) {
      x
    } else{
      prettyNum(round(x, 2), big.mark = ",")
    }
  }
)
title = paste("Assessment of", params$spp, "in", params$cntry)
```

---
title: `r title`
---

```{r dataimport}
DataFolder = paste0(params$rootDir, '/Data/derived/AnalysisExport_', params$date)
DataFiles <- list.files(DataFolder, full.names = T)

#load in raw responses
responses_path <- DataFiles[str_detect(DataFiles, 'cleaned_responses')]
responses <- read_csv(responses_path) %>% filter(sppcode==sppCode)

#load in plots of threat impact
impact_plots_path <- DataFiles[str_detect(DataFiles, cntryAbbr) & str_detect(DataFiles, sppCode) & 
                            str_detect(DataFiles, '_threat_impact_plots.RDS')]
impact_plots <- readRDS(impact_plots_path) 

#load in pooled data
pooled_data_path <- DataFiles[str_detect(DataFiles, cntryAbbr) & str_detect(DataFiles, sppCode) & 
                            str_detect(DataFiles, '_pooled.RDS')]
pooled_data <- readRDS(pooled_data_path) 

#load in plots of scope, sev, and pop data
scope_sev_path <- DataFiles[str_detect(DataFiles, cntryAbbr) & str_detect(DataFiles, sppCode) & 
                            str_detect(DataFiles, '^*[0-9].RDS$')]
scope_sev <- readRDS(scope_sev_path) 

#Table of threat lables
threats <- read.csv(paste0(params$rootDir, '/Data/ThreatNum.csv'))
```

\captionsetup[table]{labelformat=empty}
# Range Size
```{r out.width = "90%", fig.align='center'}
thisRangeFN <- paste0(params$rootDir, '/RangeGraphs/range_', params$spp, "_", params$cntry, '.png')
knitr::include_graphics(thisRangeFN)
```
\newpage

# Population Size

## Expert Elicited Values
```{r popSize_data, results='asis'}
responses %>% filter(Q_group=='pop' & Q_sub == 'Size') %>% 
  select(min, mean, max, conf, token) %>% 
  mutate(conf=paste0(conf, "%")) %>% 
  rename(central=mean,
         confidence=conf, 
         expert=token) %>% 
  select(expert, everything()) %>% 
  mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ','))) %>% 
  knitr::kable()
```

## Distribution
```{r popSize_graph}
expert_colors <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Size') %>% 
  .$value %>% flatten() %>% .$colors

expert_sizes <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Size') %>% 
  .$value %>% flatten() %>% .$expertSZ

my_plot <- scope_sev %>% filter(q_type=='popSize') %>% .$plots %>% .[[1]]

my_plot + 
    scale_color_manual(values=expert_colors) +
    scale_size_manual(values = expert_sizes) +
  theme(legend.position = 'bottom', legend.title = element_blank()) +
  guides(color=guide_legend(ncol=4)) +
  scale_x_log10(label = comma) 
```

```{r popSize_quantiles, results='asis'}
pooled_quantiles <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Size') %>% 
  .$pooled_dist %>% flatten() %>% .$pooled_Quantiles

expert_quantiles <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Size') %>% 
  .$expert_impact %>% flatten() %>% .$Quantiles %>% as_tibble()

expert_quantiles %>% bind_cols('linear pool'=pooled_quantiles) %>% 
  mutate(measure = c('Q1','Median','Q3')) %>% 
  pivot_longer(cols = !'measure') %>% 
  pivot_wider(names_from = measure, values_from = value) %>% 
  mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ','))) %>% 
  knitr::kable()
```
\newpage

# Population Trend

## Expert Elicited Values
```{r popTrend_data}
responses %>% filter(Q_group=='pop' & Q_sub == 'Trend') %>%
  select(min, mean, max, conf, token) %>%
  mutate(conf=paste0(conf, "%"),
         min=paste0(min*100, "%"),
         max=paste0(max*100, "%"),
         mean=paste0(mean*100, "%")) %>%
  rename(central=mean,
         confidence=conf,
         expert=token) %>%
  select(expert, everything()) %>%
  mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ','))) %>%
  knitr::kable()
```

## Distribution
```{r popTrend_graph}
expert_colors <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Trend') %>% 
  .$value %>% flatten() %>% .$colors

expert_sizes <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Trend') %>% 
  .$value %>% flatten() %>% .$expertSZ

my_plot <- scope_sev %>% filter(q_type=='popTrend') %>% .$plots %>% .[[1]]

my_plot + scale_color_manual(values = expert_colors) +
  scale_size_manual(values = expert_sizes) +
  theme(legend.position = 'bottom', legend.title = element_blank()) +
  guides(color = guide_legend(ncol=4)) 
```

```{r popTrend_quantiles}
pooled_quantiles <- pooled_data %>% filter(Q_group=='pop' & Q_sub=='Trend') %>% 
  .$pooled_dist %>% flatten() %>% .$pooled_Quantiles

expert_quantiles <- pooled_data %>% filter(Q_group=='pop'& Q_sub=='Trend') %>% 
  .$expert_impact %>% flatten() %>% .$Quantiles %>% as_tibble()

expert_quantiles %>% bind_cols('linear pool'=pooled_quantiles) %>% 
  mutate(measure = c('Q1','Median','Q3')) %>% 
  pivot_longer(cols = !'measure') %>% 
  pivot_wider(names_from = measure, values_from = value) %>% 
  mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ','))) %>% 
  mutate(Median=paste0(round(as.numeric(Median)*100, digits = 0), "%"),
         Q1=paste0(round(as.numeric(Q1)*100, digits = 0), "%"),
         Q3=paste0(round(as.numeric(Q3)*100, digits = 0), "%")
  ) %>% 
  knitr::kable()
```

\newpage

# Threat Assessment

Scope, Severity, and resulting population impact for IUCN level 2 threats.

If a plot is missing, data was missing from the original survey (e.g., one or more of the questions was left blank ("-").

The expert rated the threat as 'negligible' if min = 0, central = 0.5, max = 1, and conf = 99.99%"

## Total Threat Estimate for Each Expert

```{r overall_expert_threat_estimate}
threats_df <- scope_sev %>% filter(!q_type %in% c("popSize","popTrend"))
df <- data.frame()
for (i in seq(1:nrow(threats_df))){
  id <-  threats_df[i,]$dist_info_id
  ss <- threats_df[i,]$q_type
  rows_to_bind <-  threats_df[i,]$Quantiles[[1]]
  rows_to_bind <- rows_to_bind %>% mutate(threat = id, Q_ss = ss) %>% 
    select(expert, threat, Q_ss, Median)
  df <- df %>% bind_rows(rows_to_bind)
}

df %>% pivot_wider(names_from = Q_ss, values_from = Median) %>% 
  mutate(impact_estimate =Scope * Severity) %>% 
  select(-Scope, -Severity) %>% 
  pivot_wider(names_from = threat, values_from = impact_estimate) %>% 
  mutate(total_impact = rowSums(across(where(is.numeric)))) %>% 
  select(expert, total_impact) %>%
  knitr::kable(digits = 5, col.names = c("expert", "Total Impact Estimate"),
               caption = paste0("Sum of median threat estimates for each expert for ", spp, "."))
```


```{r functions}
#function to get raw responses of each expert for each threat and format table
get_responses <- function(responses, Q_group, Q_sub){
  out <- responses %>% filter(Q_group==Q_group & Q_sub==Q_sub) %>% 
  select(min, mean, max, conf, token) %>% 
  mutate(conf=paste0(conf, "%"),
         min=paste0(min*100, "%"),
         max=paste0(max*100, "%"),
         mean=paste0(mean*100, "%")) %>% 
  rename(central=mean,
         confidence=conf, 
         expert=token) %>% 
  select(expert, everything()) %>% 
  mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ',')))
  return(out)
}


#function to get and format table of quantiles for each expert and for 
#linear pool for scope and sev
get_scope_sev_QuantileTable <- function(data, Q_group, Q_sub){
  df <- data[['Quantiles']][[1]]
  #remove rownames
  rownames(df) <- NULL
  df <- df %>% as_tibble()
  q_table <- df %>% select(-P99) %>% 
    mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ','))) %>% 
    mutate(Median=paste0(round(as.numeric(Median)*100, digits = 0), "%"),
           Q1=paste0(round(as.numeric(Q1)*100, digits = 0), "%"),
           Q3=paste0(round(as.numeric(Q3)*100, digits = 0), "%")
  )
  return(q_table)
}



# function to get and format table of quantiles for each expert and for 
#linear pool for impact
get_impact_QuantileTable <- function(pooled_data, Q_group, Q_sub){
  pooled_quantiles <- pooled_data %>% 
    filter(Q_group==Q_group & Q_sub==Q_sub) %>% 
    .$pooled_dist %>% flatten() %>% .$pooled_Quantiles
  
  expert_quantiles <- pooled_data %>%
    filter(Q_group==Q_group & Q_sub==Q_sub) %>% 
    .$expert_impact %>% flatten() %>% .$Quantiles %>% as_tibble()
  
  q_table <- expert_quantiles %>% bind_cols('linear pool' = pooled_quantiles) %>% 
    mutate(measure = c('Q1','Median','Q3')) %>% 
    pivot_longer(cols = !'measure') %>% 
    pivot_wider(names_from = measure, values_from = value) %>% 
    mutate(across(where(is.numeric), ~prettyNum(.x,big.mark = ','))) %>% 
    mutate(Median=paste0(round(as.numeric(Median)*100, digits = 0), "%"),
           Q1=paste0(round(as.numeric(Q1)*100, digits = 0), "%"),
           Q3=paste0(round(as.numeric(Q3)*100, digits = 0), "%")
  )
  return(q_table)
}


#function to get and format plot of distributions for scope, sev, and impact
get_Plot <- function(scope_sev, Q_group, Q_sub){
  expert_colors <- scope_sev %>% 
    filter(Q_group==Q_group & Q_sub==Q_sub) %>% .$value %>% flatten() %>% .$colors

  expert_sizes <- scope_sev %>% 
    filter(Q_group==Q_group & Q_sub==Q_sub) %>% .$value %>% flatten() %>% .$expertSZ

  my_plot <- scope_sev %>% 
    filter(Q_group==Q_group & Q_sub==Q_sub) %>% .$plots %>% .[[1]] + 
    scale_color_manual(values = expert_colors) +
    scale_size_manual(values = expert_sizes) +
    theme(legend.position = 'bottom', legend.title = element_blank()) +
    guides(color = guide_legend(ncol=4))
  return(my_plot)
}
```



```{r ThreatsStuff}
#prep threat data for looping
TData <- scope_sev %>%
  separate(dist_info_id, into=c('Q_group','Q_sub'), sep = "_") %>% 
  filter(Q_group != 'pop')

threat_responses <- responses %>% filter(Q_group!='pop')

#make somewhere to store all threat objects as they are created
allThreats_stuff <- TData %>% 
  select(Q_group, Q_sub) %>% 
  distinct() %>% 
  plyr::dlply(., 'Q_group', .fun=function(df){
   plyr::dlply(df, 'Q_sub', .fun=function(df){
     list()
     }) 
  })

TData <- split(TData, TData$Q_group)
TAnalysis <- split(pooled_data, pooled_data$Q_group)

for (gN in names(TData)) {
  #list of subthreats for the threat to iterate through
  subTs <- threats %>% filter(Q_group==gN) %>% .$Q_sub %>% unique()
  
  #filter data down to threat group
  gT1 <- unique(threats[threats$Q_group == gN, 'Threat'])
  thisT1 <- TData[[gN]]
  thisT2 <- TAnalysis[[gN]]
  t_responses <- threat_responses %>% filter(Q_group==gN)
  t_impact_plots <- impact_plots %>% filter(Q_group==gN)

  for (sT in subTs) {

    #filter data down to subthreat group
    ThisThreat <- thisT1 %>% filter(Q_sub == sT)
    ThisTImpact <- thisT2 %>% filter(Q_sub == sT)
    this_t_response <- t_responses %>% filter(Q_sub==sT)
    this_t_impact_plot <- t_impact_plots %>% filter(Q_sub==sT)
    
    #Table of raw data for scope
    t_response_scope <- this_t_response %>% filter(Q_ss == 'Scope')
    D_scope <- get_responses(t_response_scope, gN, sT)
    
    #Table of raw data for severity
    t_response_sev <- this_t_response %>% filter(Q_ss == 'Severity')
    D_severity <- get_responses(t_response_sev, gN, sT)
    
    #Plot of scope and severity distributions
    scope_plot_data <- ThisThreat %>% filter(q_type=='Scope')
    scope_plot <- get_Plot(scope_plot_data, gN, sT)
    
    sev_plot_data <- ThisThreat %>% filter(q_type=='Severity')
    sev_plot <- get_Plot(sev_plot_data, gN, sT)
    
    scope_sev_plots <- ggarrange(scope_plot, sev_plot, common.legend=T)
    
    #table of quantiles of scope
    q_scope_data <- ThisThreat %>% filter(q_type=='Scope')
    Q_scope <- get_scope_sev_QuantileTable(q_scope_data, gN, sT)

    #table of quantiles of severity
    q_sev_data <- ThisThreat %>% filter(q_type=='Severity')
    Q_sev <- get_scope_sev_QuantileTable(q_sev_data, gN, sT)


    #plot of Impact
    p_Impact <- get_Plot(this_t_impact_plot, gN, sT)

    #table of quantiles of impact
    Q_Impact <- get_impact_QuantileTable(ThisTImpact, gN, sT)
    
    allThreats_stuff[[gN]][[sT]]=list(rawScope=D_scope,
                                       rawSeverity=D_severity,
                                       DistPlot=scope_sev_plots,
                                       quantileScope=Q_scope,
                                       quantileSeverity=Q_sev,
                                       ImpactPlot=p_Impact,
                                       quantileImpact=Q_Impact)
  }
}
```


```{r displayResults, results='asis'}
for(T1 in unique(threats$Q_group)) {
  
  #T1 Heading
  cat('  \n## ', T1, '  \n')
  
  for (T2 in names(allThreats_stuff[[T1]])) {
    #T2 Heading
    cat('  \n### ', T2, '  \n')
    
    cat('  \n#### ', 'Expert Elicited Values', '  \n')
    
    cat("\n\n")
    
            cat("\\",
          c(
             "\\begin{table}[!htb]
                    \\caption{Scope}
                    \\centering",
                    knitr::kable(allThreats_stuff[[T1]][[T2]]$rawScope, format='latex', booktabs=T),
             "\\end{table}"
          )
        )
            
                cat("\\",
          c(
             "\\begin{table}[!htb]
                  \\centering
                  \\caption{Severity}",
                  knitr::kable(allThreats_stuff[[T1]][[T2]]$rawSeverity, format='latex', booktabs=T) ,
             "\\end{table}"
          )
        )

        print(allThreats_stuff[[T1]][[T2]]$DistPlot)

        cat("  \n\n") 

        cat("\n\n")
        
                    cat("\\",
          c(
             "\\begin{table}[!htb]
                    \\caption{Scope}
                    \\centering",
                    knitr::kable(allThreats_stuff[[T1]][[T2]]$quantileScope, format='latex', booktabs=T),
             "\\end{table}"
          )
        )
            cat("\n\n")
            
            cat("\n\n")
            
                cat("\\",
          c(
             "\\begin{table}[!htb]
                  \\centering
                  \\caption{Severity}",
                  knitr::kable(allThreats_stuff[[T1]][[T2]]$quantileSeverity, format='latex', booktabs=T) ,
             "\\end{table}"
          )
        )
        
        cat("\n\n")
        cat("\n\n\\pagebreak\n")
        # cat("  \n")#end Elicit heading
        
    cat('#### ', 'Impact', '  \n')
     cat("\n\n")

        cat("\\",
          c("\\begin{table}[!htb]
                    \\caption{Impact}
                    \\centering",
                    knitr::kable(allThreats_stuff[[T1]][[T2]]$quantileImpact, format='latex', booktabs=T),
            "\\end{table}"
            )
          )
        
        cat("  \n")
        cat("\n\n")
        print(allThreats_stuff[[T1]][[T2]]$ImpactPlot)
        cat("  \n\n")
        cat("\n\n\\pagebreak\n")
        

  } #end T2
  cat("  \n") #End T1 heading
  cat("\n\n\\pagebreak\n")
} #end T1
```
